### 2017-03-06 Writing/draft.tex
corrected proof for equation 3

For any $n \in [1;\infty)$ and $x_{n} = y_{n}$ then:
%TG: Is that valid for a demonstration?
\begin{equation}
    \label{identitydemo}
    \begin{aligned}
    \abs{x_{n}-y_{n}} &= 0\\
    \sum_{i}^{n}\abs{x_{i}-y_{i}} &= 0\\
    \frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n} &= 0\\
    \abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}} &= 0\\
    \frac{\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}}}{\frac{1}{2}} &= 0\\
    1 - \left(\frac{\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}}}{\frac{1}{2}}\right) &= 0\\
    \end{aligned}
\end{equation}

@@

As described in equations \ref{Positivity}, \ref{Identity} and \ref{Equality},

\begin{equation}
    \label{subadditivity_demo}
    \begin{aligned}
    &0\leq CD_{x,z} \leq 1\\
    &\text{and}\\
    &0\leq CD_{z,y} \leq 1\\
    &\text{thus}\\
    &0\leq CD_{x,z} + CD_{z,y}  \leq 2\\
    \end{aligned}
\end{equation}

\subsubsection{Case 1}
If $CD_{x,z} = 0$, then, following \ref{Identity}:

\begin{equation}
    \label{subadditivity_demo_case1}
    \begin{aligned}
    &CD_{x,z} = CD_{z,y} = CD_{x,y}\\
    &\text{then}\\
    &CD_{x,y} \leq CD_{x,z} + CD_{z,y}\\
    \end{aligned}
\end{equation}

\subsubsection{Case 2}
If $CD_{x,z} > 0$, then:

\begin{equation}
    \label{subadditivity_demo_case2}
    \begin{aligned}
    &CD_{x,z} = CD_{z,y} = CD_{x,y}\\
    &\text{then}\\
    &CD_{x,y} \leq CD_{x,z} + CD_{z,y}\\
    \end{aligned}
\end{equation}

>>>>

For any $n \in [1;\infty)$ and $x_{n} = y_{n}$ then:
%TG: Is that valid for a demonstration?
\begin{equation}
    \label{identitydemo}
    \begin{aligned}
    \abs{x_{n}-y_{n}} &= 0\\
    \sum_{i}^{n}\abs{x_{i}-y_{i}} &= 0\\
    \frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n} &= 0\\
    \abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}} &= \frac{1}{2}\\
    \frac{\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}}}{\frac{1}{2}} &= 1\\
    1 - \left(\frac{\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}}}{\frac{1}{2}}\right) &= 0\\
    \end{aligned}
\end{equation}

@@

% As described in equations \ref{Positivity}, \ref{Identity} and \ref{Equality},

% \begin{equation}
%     \label{subadditivity_demo}
%     \begin{aligned}
%     &0\leq CD_{x,z} \leq 1\\
%     &\text{and}\\
%     &0\leq CD_{z,y} \leq 1\\
%     &\text{thus}\\
%     &0\leq CD_{x,z} + CD_{z,y}  \leq 2\\
%     \end{aligned}
% \end{equation}

% \subsubsection{Case 1}
% If $CD_{x,z} = 0$, then, following \ref{Identity}:

% \begin{equation}
%     \label{subadditivity_demo_case1}
%     \begin{aligned}
%     &CD_{x,z} = CD_{z,y} = CD_{x,y}\\
%     &\text{then}\\
%     &CD_{x,y} \leq CD_{x,z} + CD_{z,y}\\
%     \end{aligned}
% \end{equation}

% \subsubsection{Case 2}
% If $CD_{x,z} > 0$, then:

% \begin{equation}
%     \label{subadditivity_demo}
%     \begin{aligned}
    % CD_{x,y} &\leq CD_{x,z} + CD_{z,y}\\
    % 1 - \left(\frac{\abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}}}{\frac{1}{2}}\right) 
    %  &\leq 
    %  1 - \left(\frac{\abs*{\frac{\sum_{k}^{j}\abs{x_{k}-y_{k}}}{j}-\frac{1}{2}}}{\frac{1}{2}}\right) 
    %  +
    %  1 - \left(\frac{\abs*{\frac{\sum_{a}^{b}\abs{x_{a}-y_{a}}}{b}-\frac{1}{2}}}{\frac{1}{2}}\right) \\
    % \abs*{\frac{\sum_{i}^{n}\abs{x_{i}-y_{i}}}{n}-\frac{1}{2}}}} 
    %  &\geq 
    %  \abs*{\frac{\sum_{k}^{j}\abs{x_{k}-y_{k}}}{j}-\frac{1}{2}}}} 
    %  +
    %  \abs*{\frac{\sum_{a}^{b}\abs{x_{a}-y_{a}}}{b}-\frac{1}{2}}}} - 2\\

     % Add brackets symbols

     % \in[0,\frac{1}{2}] &\geq (-2) \in[0,\frac{1}{2}] \in[0,\frac{1}{2}]\\
     % \in[0,\frac{1}{2}] &\geq \in[-2,-1]\\

%     \end{aligned}
% \end{equation}
